Correlating Scanning Ion Conductance and Super-Resolved Fluorescence Microscopy

### 2020-10-09 sections/correlated-sicm-and-fm.tex
Update correlated-sicm-and-fm.tex

>>>>

%work in progress / noch nicht fertig
By combining SICM and surface scanning confocal microscopy or scanning surface confocal
microscopy (SSCM) \cite{Gorelik2002} two scanning microscopy techniques are combined enabling 
simultaneous imaging of the same region on the same sample at the same time. To achieve matching 
field of views, pixel sizes and recording times consequentially yielding two correlating data sets
two slightly different setups are imaginable and have been put to the test (see figure \ref{fig:sicm+sscm_setup}) 
\cite{Gorelik2002}\cite{Shevchuk2013}.
\begin{figure}
  \includegraphics[width=\textwidth]{gr/correlating/sicm+sscm_setup}
  \caption{%
    \textbf{Two possible setups for a combined SIC and SSC microscope.}
    \textbf{a:}
    \textbf{b:} 
    Reprinted with permission from ref \cite{Shevchuk2013}.
  }
  \label{fig:sicm+sscm_setup}
\end{figure}
